Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-30 demystify.tex
updates

\subsection{Waiving Your Right}  Choosing not to look at a reference letter is pretty standard in school and job applications. When you waive your right to see the letter, it adds a layer of trust, showing you're confident in your choice of referees and that you're not trying to twist their words. It's also about keeping things open and honest between you and your letter writers and encourages them to be real about your strengths and qualifications. Plus, it keeps things private.

@@

If a student asks me to write letter for them, I will agree as I believe it is part of my job.  However, I will let them know if I won't be able to write a strong letter for them (e.g., they just take my class and I don't know them well enough), and suggest they find someone else.  If they insist, then I will write the letter. It will be a weak and generic letter though I still try to have something positive, e.g., the student is hardworking, or that I heard they are working on a research project, etc.  Regardless, the letters will still be short and weak (\autoref{sec:generic-letters}) and usually take about 5--10 minutes to write.

>>>>

\subsection{Waiving Your Right}\label{sec:waive-right}

When you ask someone to write a letter for you, you will be asked if you want to waive your right to see the letter.  You should \emph{always} waive your right.

Choosing not to look at a reference letter is pretty standard in school and job applications. When you waive your right to see the letter, it adds a layer of trust, showing you're confident in your choice of referees and that you're not trying to twist their words. It's also about keeping things open and honest between you and your letter writers and encourages them to be real about your strengths and qualifications. Plus, it keeps things private.

@@

If a student asks me to write letter for them, I will agree as I believe it is part of my job. However, I will ask them to waive their right to see the letter (\autoref{sec:waive-right}), and will not write if they do not do so.

I will also let the student know if I can write a strong letter for them.  If I can't, I will tell them and suggest they find someone else.  If they insist, then I will write for them. While I try to say something positive, e.g., the student is hardworking, or that I heard they are working on a research project, etc, the letter will still be short and weak (\autoref{sec:generic-letters}). Usually it takes me about 5--10 minutes to write such a letter.
